Light Transport Techniques for Tensor Field Visualization

### 2019-07-30 beamer2thesis/dummy.tex
update

%\usepackage[ngerman]{babel}
%\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{ulem}
\usepackage{makecell}
\usepackage{upgreek}
\usepackage{movie15}
%\usepackage{xcolor}
%\usepackage{isodate}
\hypersetup{colorlinks,linkcolor=black,urlcolor=black}
\addto{\captionsngerman}{%
  \renewcommand*{\contentsname}{Contents}
  \renewcommand*{\listfigurename}{Figures}
  \renewcommand*{\listtablename}{Tables}
  \renewcommand*{\figurename}{Fig.}	
  \renewcommand*{\tablename}{Tab.}
}
\newcommand*\mean[1]{\bar{#1}}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\newcommand\widebar[1]{\mathop{\overline{#1}}}

@@

%\color{unirot}{sebibek@gmail.com}
%\newsubfloat{figure}
\newcommand{\source}[1]{\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{Source: \color{black}{#1}}}}}
\setlength{\belowcaptionskip}{-10pt}
\setlength{\intextsep}{-20pt}

\begin{document}

@@

\frame{
\frametitle{{Propagation Scheme - Physical Model}}
\begin{block}{\centering \textbf{Crystal Fiber Structures}}
\begin{itemize}
	\item crystal lattices reveal gradients dependent on direction, which leads to anisotropic light transport inside the medium (birefringence)
	\item the propability for redistribution of a photon in a particular direction is given by the phase function model yielded from Rayleigh scattering:
	\begin{align*}
 	P(\omega) &= \frac{T(\omega)}{\int_{k\pi}^{(k+1)\pi}T(\omega)\mathop{d\omega}}\\
 	\mathit{with} \int_0^{\pi} P(\omega) &= 1.
	\end{align*}
	\item each tensor is then a unique footprint: $t_{i,j}\mapsto T(\omega)$
\end{itemize}
\end{block}
} % END OF FRAME

>>>>

%\usepackage[ngerman]{babel}
%\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{ulem}
\usepackage{makecell}
\usepackage{upgreek}
\usepackage{movie15}
%\usepackage{xcolor}
%\usepackage{isodate}
\hypersetup{colorlinks,linkcolor=black,urlcolor=black}
\addto{\captionsngerman}{%
  \renewcommand*{\contentsname}{Contents}
  \renewcommand*{\listfigurename}{Figures}
  \renewcommand*{\listtablename}{Tables}
  \renewcommand*{\figurename}{Fig.}	
  \renewcommand*{\tablename}{Tab.}
}
\newcommand*\mean[1]{\bar{#1}}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\newcommand\widebar[1]{\mathop{\overline{#1}}}
\usepackage{caption}
\captionsetup{font=scriptsize}

@@

%\color{unirot}{sebibek@gmail.com}
%\newsubfloat{figure}
\newcommand{\source}[1]{\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{Source: \color{black}{#1}}}}}
\setlength{\belowcaptionskip}{-10pt}
\setlength{\intextsep}{-20pt}
%\usepackage[style=verbose,backend=biber]{biblatex}
%\addbibresource{references.bib}
%\usepackage[multiple]{footmisc}
%\usepackage[bottom]{footmisc}
\renewcommand\thempfootnote{\arabic{mpfootnote}}
\begin{document}

@@

\frame{
\frametitle{{Eigenanalysis - Tensor Fields}}
\begin{columns}
\begin{column}{.6\textwidth}
Direction, invariant under transformation $A$, sought:
\begin{block}{\centering \textbf{Eigenvalue Problem}}
\begin{align*}
	A \cdot \boldsymbol{\epsilon} = \lambda \boldsymbol{\epsilon}
\end{align*}
with: $A$: square matrix, $\lambda$: eigenvalue $\mathbf{\epsilon}$: eigenvector
\end{block}
\begin{itemize}
	\item eigensystems:\\ full set of eigenvalues and -vectors
	\item we propose to use singular value systems (SVS) in analogy to Eigensystems\\
	{\tiny Proof: "Glyphs for General Second-Order 2D and 3D Tensors", Gerrits et al., 2017}
\end{itemize}
\end{column}
\begin{column}{.4\textwidth}
\begin{figure}[t]
\begin{minipage}{0.85\textwidth}
\includegraphics[width=\textwidth]{HAT_edit2.png}
\caption*{Eigensystem: characteristic ellipsoid}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\source{\url{https://slideplayer.com/slide/5291764}}
\end{minipage}

\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

\frame{
\frametitle{{Computation of Eigensystem - Tensor Fields}}

\begin{columns}
\begin{column}{.6\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Matrix Decompositions}}
1) Eigenvalue Decomposition: \hskip 46pt
$
	A = {R}{S}{R}^*
$\\
2) Singular Value Decomposition (SVD): 
$
	{A} = {U} {\Sigma} {V}^*
$
\end{block}
\end{small}
\begin{small}
\begin{enumerate}
	\item eigenvalues \hskip 14pt and eigenvectors
	\item singular values and singular vectors (SVs)
\end{enumerate}
\begin{itemize}
	\item SVs represent the axes of characteristic ellipsoid \footnote{Gerrits et al. ''Glyphs for General Second-Order 2D and 3D Tensors", IEEE Transactions on Visualization and Computer Graphics, 2017.}
	\item singular values ($s_i=\sqrt{\lvert\lambda_i\rvert}$)\footnote{M. Kieburg, “What is the Relation between Eigenvalues \& Singular
Values?, 2016} are lengths of axes
\end{itemize}
\end{small}

\end{column}
\begin{column}{.4\textwidth}
\begin{figure}[t]
\begin{minipage}{0.9\textwidth}
\includegraphics[width=\textwidth]{SVD.png}
\caption*{Singular value system}
\end{minipage}
\begin{minipage}{0.05\textwidth}
\source{\url{https://w.wiki/6WN}}
\end{minipage}
\end{figure}

\end{column}
\end{columns}
} % END OF FRAME
